\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://maxwellpaulm.github.io/}{\Large Paul Maxwell}} & \href{mailto:maxwellpaulm@gmail.com}{maxwellpaulm@gmail.com}\\
  & (415) 944-0822 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science; GPA: 4.00}{Aug 2021 -- Present}
    \resumeSubheading
      {University of Michigan, College of Engineering}{Ann Arbor, MI}
      {Bachelor of Science in Engineering in Computer Science, Minor in Mathematics}{Aug 2014 -- Apr 2018}
      {Graduated cum laude, Dean's List (Dec 2017, Apr 2018); GPA: 3.375/4.0}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    %-----------Ampla-----------------
    \resumeSubheading
      {Ampla Technologies}{New York, NY}
      {Data Engineer}{Mar 2022 - Present}
      \resumeItemListStart
        \resumeItem{Tensorflow}
          {TensorFlow is an open source software library for numerical computation using data flow graphs; primarily used for training deep learning models. Worked on APIs and performance for training models on Tensor Processing Units (TPU).}
        \resumeItem{Apache Beam}
          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines, as well as a set of language-specific SDKs for constructing pipelines and runners.}
      \resumeItemListEnd

    %-----------BlackRock-----------------
    \resumeSubheading
      {BlackRock}{New York, NY}
      {Associate Software Engineer - Aladdin Product Group, New York, NY}{Jan 2021 - Mar 2022}
      \resumeItemListStart
        \resumeItem{}{Engineering the next generation of portfolio construction tools through a highly scalable distributed system capable of tolerating 100x the load of the previous system by using a map-reduce process.}
        \resumeItem{}{Led the design and implementation of a service using gRPC and requiring the coordination of multiple teams.}
        \resumeItem{}{Architected a service to track and compare important metrics from different products and led a team of three interns in the development of the server and the client.}
        \resumeItem{}{Developed a Python tool to compare prime and beta releases for differences in the data they serve.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Analyst Software Engineer - Aladdin Product Group, New York, NY}{Sep 2020 - Dec 2020}
      \resumeItemListStart
        \resumeItem{}{Designed and built a load testing tool for a server-based portfolio construction service using Locust.}
        \resumeItem{}{Enhanced a distributed process to optimize the frequency at which cached composite benchmarks are refreshed.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Rotational Analyst Software Engineer - Aladdin Product Group, San Francisco, CA}{Jul 2018 - Aug 2020}
      \resumeItemListStart
        \resumeItem{}{Rotated through four teams involved in software and data engineering topics.}
        \resumeItem{}{Implemented alpha signals for quantitative active equity researchers in Python using Pandas and NumPy.}
        \resumeItem{}{Enhanced a multi-asset portfolio construction tool by implementing dynamic benchmarking and allowing for fixed or floating weights to be assigned to indices and model assets, along with nested indices.}
        \resumeItem{}{Developed an automated testing framework for the systematic active equity engineering team to ensure signal fidelity.}
        \resumeItem{}{Created a Python library for systematic fixed income researchers to enable easy access to more natural language processing analytics using Apache Spark while delivering runtime performance improvements of 15-20\%.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Summer Analyst Software Engineer - Aladdin Product Group, San Francisco, CA}{Summer 2017}
      \resumeItemListStart
        \resumeItem{}{Designed and built a service to help portfolio managers and developers query index projection errors}
      \resumeItemListEnd

    %-----------Workday-----------------
    \resumeSubheading
      {Workday}{Pleasanton, CA}
      {Software Engineering Intern}{Summer 2016}
      \resumeItemListStart
        \resumeItem{}
          {Redesigned the auto-generation of business process model definitions resulting in a streamlined user experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{TBD}{TBD}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages: }{Python, Java, C++, C, Scala, R, Typescript}
     \hfill
     \textbf{Technologies: }{Docker, Kubernetes, Apache Airflow, GCS, BigQuery, DBT, Apache Spark, Angular, Postgres}
   }
 \resumeSubHeadingListEnd

%--------CREDENTIALS------------
\section{Credentials}
\resumeSubHeadingListStart
\resumeSubheading
    {Harvard Business School Online}{Cambridge, MA}
    {CORe Credential of Rediness, Pass with High Honors}{Jun 2018}
\resumeSubheading
  {Chartered Financial Analyst (CFA) Charterholder}{}
  {}{}
\resumeSubheading
  {Associate of the Society of Actuaries (Candidate)}{}
  {Financial Mathematics, Investment and Financial Markets, Probability, Statistics for Risk Modeling}{}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}