\documentclass[letterpaper,10pt]{article}

\usepackage{mathptmx}
\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}, \small{#2} & \small{#3} \\
      \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[1]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://maxwellpaulm.github.io/}{\Large Paul Maxwell}} & \href{mailto:maxwellpaulm@gmail.com}{\small maxwellpaulm@gmail.com}\\
  \small{59 West 74th Street, Apt. 2B, New York, NY 10023} & \small {(415) 944-0822}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology, College of Computing}{Atlanta, GA}{Aug 2021 -- Aug 2023}
      {Master of Science in Computer Science; GPA: 4.0}
    \resumeSubheading
      {University of Michigan, College of Engineering}{Ann Arbor, MI}{Aug 2014 -- Apr 2018}
      {Bachelor of Science in Engineering in Computer Science, Minor in Mathematics; GPA: 3.375}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    %-----------Ampla-----------------
    \resumeSubheading
      {Ampla Technologies}{New York, NY}{Mar 2022 - Present}
      {Data Engineer}
      \resumeItemListStart
        \resumeItem{Working as an engineer at a fin-tech series-A startup, where I partner with the risk team to automate processes, ingest financial data, and generate insightful metrics into small businesses.}
        \resumeItem{Architected an automated underwriting process for brands to apply for funding along with a senior data scientist.}
        \resumeItem{Improved and rewrote a core banking data integration to run 25x faster than the original while using less than 1\% of the original compute resources.}
      \resumeItemListEnd

    %-----------BlackRock-----------------
    \resumeSubheading
      {BlackRock}{New York, NY}{Summer 2017; Jul 2018 -- Mar 2022}
      {Associate Software Engineer, New York, NY (Jan 2021 - Mar 2022)}
      \resumeItemListStart
        \resumeItem{Engineered the next generation of portfolio construction tools through a highly scalable distributed system capable of tolerating 100x the load of the previous system by using a map-reduce process.}
        \resumeItem{Led the design and implementation of a service using gRPC and requiring the coordination of multiple teams.}
        \resumeItem{Architected a service to track and compare important metrics from different products and led a team of three interns in the development of the server and the client.}
        \resumeItem{Developed a Python tool to compare prime and beta releases for differences in the data they serve.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Analyst Software Engineer, New York, NY (Sep 2020 - Dec 2020)}
      \resumeItemListStart
        \resumeItem{Designed and built a load testing tool for a server-based portfolio construction service using Locust.}
        \resumeItem{Enhanced a distributed process to optimize the frequency at which cached composite benchmarks are refreshed.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Rotational Analyst Software Engineer, San Francisco, CA (Jul 2018 - Aug 2020)}
      \resumeItemListStart
        \resumeItem{Rotated through four teams involved in software and data engineering topics.}
        \resumeItem{Implemented alpha signals for quantitative active equity researchers in Python using Pandas and NumPy.}
        \resumeItem{Enhanced a multi-asset portfolio construction tool by implementing dynamic benchmarking and allowing for fixed or floating weights to be assigned to indices and model assets, along with nested indices.}
        \resumeItem{Developed an automated testing framework for the systematic active equity engineering team to ensure signal fidelity.}
        \resumeItem{Created a Python library for systematic fixed income researchers to enable easy access to more natural language processing analytics using Apache Spark while delivering runtime performance improvements of 15-20\%.}
      \resumeItemListEnd
      \resumeSubSubheading
      {Summer Analyst Software Engineer, San Francisco, CA (Summer 2017)}
      \resumeItemListStart
        \resumeItem{Designed and built a service to help portfolio managers and developers query index projection errors}
      \resumeItemListEnd

    %-----------Workday-----------------
    \resumeSubheading
      {Workday}{Pleasanton, CA}{Summer 2016}
      {Software Engineering Intern}
      \resumeItemListStart
        \resumeItem{Redesigned the auto-generation of business process model definitions resulting in a streamlined user experience.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{TBD}{\href{https://github.com/maxwellpaulm}{\small GitHub: maxwellpaulm}}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \item{\textbf{Languages: }{Python, Java, C++, C, Scala, R, Typescript}}
    \item{\textbf{Technologies: }{Docker, Kubernetes, Apache Airflow, GCS, BigQuery, DBT, Apache Spark, Angular, Postgres}}
 \resumeSubHeadingListEnd

% %--------CREDENTIALS------------
% \section{Credentials}
% \resumeSubHeadingListStart
% \resumeSubheading
%     {Harvard Business School Online}{Cambridge, MA}
%     {CORe Credential of Rediness, Pass with High Honors}{Jun 2018}
% \resumeSubheading
%   {Chartered Financial Analyst (CFA) Charterholder}{}
%   {}{}
% \resumeSubheading
%   {Associate of the Society of Actuaries (Candidate)}{}
%   {Financial Mathematics, Investment and Financial Markets, Probability, Statistics for Risk Modeling}{}
% \resumeSubHeadingListEnd


%--------LEADERSHIP------------
\section{Leadership}
\resumeSubHeadingListStart
\resumeSubheading
    {Theta Chi Fraternity, University of Michigan}{Ann Arbor, MI}{Sep 2014 - Apr 2018}
    {President of Alpha Gamma Chapter (Sep 2015 - Sep 2016)}
    \resumeItemListStart
      \resumeItem{Managed a chapter with over 90 men, acted as the lead correspondent with the alumni board and national fraternity responsible for building and maintaining working relationships and aligning chapter values.}
      \resumeItem{Directed the chapter's Executive Committee as President, led discussions and votes on internal decisions governing chapter members and appointed a risk manager to the committee to help ensure safety and responsibility.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}